Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-03 article.tex
bookmark

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
Figure~\ref{fig:cross_sections} plots the intensity profile in two lateral
cross sections of the viewed field, extracted from the images in
\cref{fig:simulation-results1}(d) and the corresponding MC derived photograph.
These plots demonstrate consistency in these cases, for most pixels.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering and MC forward models. 
    (a) cross sections of low density simulations (\cref{fig:simulation-results1}(d)
    and \cref{fig:simulation_particles}(a)). (b) cross sections of
    high density simulations (\cref{fig:simulation_particles}(d)).
  }
  \label{fig:cross_sections}
\end{figure}

@@

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as MC simulations show, it is
important to generalize the recovery algorithm so that high-order scattering 
is included in it. Such generalization would be computationally complex: 
in our tests, the MC forward model was slower by 2-3 orders of magnitude than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering model requires research into
numerical schemes for increasing the solution efficiency of both forward and inverse problems.  
The remote sensing community has devised several approaches to better approximate multiple-scattering problems, mainly in 1D scenes. These include successive orders of scattering, DISORT..... We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications~\cite{Pust2011} should be
set to optimally recover a wide range of aerosol distributions.
\hl{The relation between the quantity and spatial distribution of
  cameras and the quality of reconstruction should also be determined.}
\fix{This requires}{These open questions require} a major theoretic
 and numerical research.

>>>>

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}(a).
\Cref{fig:cross_sections} plots the intensity profile
along a horizontal cross section of the viewed field, 
comparing photographs simulated using the single-scattering and the  MC forward models.
\Cref{fig:cross_sections}(a) compares photographs \cref{fig:simulation-results1}(d)
and \cref{fig:simulation_particles}(a) of the {\em Haze Blobs} scene.
This plot demonstrates consistency in this scene, for most pixels.
\Cref{fig:cross_sections}(b) compares photographs of the {\em Haze Blobs} scene
where the aerosol density was increased ten folds (see \cref{sec:optimization-results}
and the corresponding MC photograph \cref{fig:simulation_particles}(d)). 
In this plot the single-scattering and MC cross sections diverge
due to the effect of the high order scattering.
\begin{figure}[t]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross-sections along the $X$-axis of photographs rendered
    by the single-scattering and MC forward models. 
    (a) cross sections of the low density scene (\cref{fig:simulation-results1}(d)
    and \cref{fig:simulation_particles}(a)). (b) cross sections of
    the high density scene (\cref{fig:simulation_particles}(d)).
  }
  \label{fig:cross_sections}
\end{figure}

@@

The estimation algorithm
uses a single scattering model. This approximation is valid when the
optical depth is small. However, as MC simulations show, it is
important to generalize the recovery algorithm so that high-order scattering 
is included in it. Such generalization would be computationally complex: 
in our tests, the MC forward model was slower by 2-3 orders of magnitude
than a single-scattering analytic model. Thus, inverting a 3D multiple-scattering
model requires research into numerical schemes for increasing the solution
efficiency of both forward and inverse problems.  
The remote sensing community has devised several approaches to better approximate
multiple-scattering problems, mainly in 1D scenes (e.g. successive
orders of scattering and discrete ordinates method). We may tap into some of these approaches.
Deploying an experimental system will be needed: camera specifications~\cite{Pust2011}
should be set to optimally recover a wide range of aerosol distributions.
\hl{The relation between the quantity and spatial distribution of
  cameras and the quality of reconstruction should also be determined.}
\fix{This requires}{These open questions require} a major theoretic
 and numerical research.
